---
title: "WA DOC Purple Air Monitor Co-Location QA"
output:
  word_document: default
  html_document: default
date: "`r Sys.Date()`"
---

## Setup tasks

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
knitr::opts_chunk$set(fig.width=8, fig.height=4) 
```

### Clear environment

```{r, include=FALSE}
# Clear environment
rm(list = ls(all = TRUE))
if (!is.null(sessionInfo()$otherPkgs)) {
  res <- suppressWarnings(
    lapply(paste('package:', names(sessionInfo()$otherPkgs), sep=""),
           detach, character.only=TRUE, unload=TRUE, force=TRUE))
}
```

### Load packages

```{r,include=FALSE}
# Load packages, installing if needed
if (!requireNamespace("pacman", quietly = TRUE))
  install.packages("pacman")
pacman::p_load(
  here,
  dplyr,
  tidyr,
  tidyverse,
  ggplot2,
  MetBrewer,
  stringr,
  data.table,
  ggpubr,
  zoo
)
```

### Make functions

```{r,include=FALSE}
# Functions for reading in co-location datasets and getting sensor names
read_and_name_csv <- function(file_path) {
  # Extract folder and file name without extension
  folder_name <- dirname(file_path) %>% basename()
  file_name <- basename(file_path) %>% tools::file_path_sans_ext()
  
  # Create the name for the data frame
  df_name <- paste(folder_name, file_name, sep = "_")
  
  # Read the CSV file
  df <- read.csv(file_path)
  
  # Assign the data frame to the global environment with the constructed name
  assign(df_name, df, envir = .GlobalEnv)
}

#Get sensor name function from the folder name
get_sensor_name <- function(df_name) {
  sensor_name <- str_sub(df_name, start = -30, end = -14)
  sensor_name
}

```

## Read in Nephelometer data

```{r,include=FALSE}
#read in the nephelometer data - data pulled from https://secure.pscleanair.org/airgraphing
neph428_513 <- read_csv(here("Duwamish4_28-5_13all.csv"), skip = 8)
neph513_520 <- read_csv(here("Duwamish5_13-5_20all.csv"), skip = 8)
neph520_601 <- read_csv(here("Duwamish5_20-6_1all.csv"), skip = 8)

#clear out site name from columns
colnames(neph428_513) <- gsub("\\s", "", sub(" - 1Hr Avg", "", sub("Seattle Duwamish Vly - ", "", colnames(neph428_513))))
colnames(neph513_520) <- gsub("\\s", "", sub(" - 1Hr Avg", "", sub("Seattle Duwamish Vly - ", "", colnames(neph513_520))))
colnames(neph520_601) <- gsub("\\s", "", sub(" - 1Hr Avg", "", sub("Seattle Duwamish Vly - ", "", colnames(neph520_601))))

colnames(neph428_513) <- gsub("-", "_", gsub("/", "_", colnames(neph428_513)))
colnames(neph513_520) <- gsub("-", "_", gsub("/", "_", colnames(neph513_520)))
colnames(neph520_601) <- gsub("-", "_", gsub("/", "_", colnames(neph520_601)))

#parse date/time
neph428_513$DateTime <- as_datetime(neph428_513$ObservationTime, tz="US/Pacific", format = "%m/%d/%Y %I:%M:%S %p")
neph513_520$DateTime <- as_datetime(neph513_520$ObservationTime, tz="US/Pacific", format = "%m/%d/%Y %I:%M:%S %p")
neph520_601$DateTime <- as_datetime(neph520_601$ObservationTime, tz="US/Pacific", format = "%m/%d/%Y %I:%M:%S %p")

#make list of all neph data
all_neph <- list(neph428_513, neph513_520, neph520_601)

#renaming variables
all_neph <- lapply(1:length(all_neph), FUN = function(i){
  all_neph[[i]] %>% rename(scat_coeff_A1000 = "LightScatEc2_bscat10e_4",
         atmos_pressure = "AmbPres_kPa", 
         Pm25Neph_ug_m3 = "Pm25Neph_ug_m3")
})

#convert b-scat to PM2.5 - per Tim 
all_neph <- lapply(1:length(all_neph), FUN = function(i){
  all_neph[[i]] <- all_neph[[i]] %>% mutate (npm25_LFP =(25.863*(scat_coeff_A1000)) + 0.7)
})
```

---

# 4/28/26 - 5/13/26 Co-Location

## Load and process PA files

### load 4-28 through 5-13 files
```{r, message=FALSE, warning=FALSE}
# List of CSV files that we want from this folder (CHANGE THIS PER FOLDER)
all_files <- list.files(here(), recursive = TRUE)
csv_files <- all_files[grepl("^CoLo1_28Apr-13May/.*/.*\\.csv$", all_files)]
unique_sensors <- unique(get_sensor_name(csv_files))

#merge all the data for selected colocation period
mydatalist <- lapply(1:length(csv_files), FUN = function(i){
  read_and_name_csv(csv_files[i])
})
mydata <- rbindlist(mydatalist)

#parse date/time
mydata$DateTime <- as_datetime(mydata$UTCDateTime,tz="US/Pacific")
```

### process chanel averages
```{r,include=FALSE}
# average channel a and channel b
mydata[, pm25ave := rowMeans(.SD), 
       by = c("mac_address", "UTCDateTime"), 
       .SDcols = c("pm2_5_atm","pm2_5_atm_b") ]

# create separate table that is just week avg & sd data, mac address
myavemac <- mydata[ ,list(weekavepm25 =  mean(pm25ave),
                          weeksdpm25 = sd(pm25ave) ), 
                    by = c("mac_address")]

#average PM2.5 data over time -- TO-DO, THE BELOW DIDN'T WORK
#sensoravemac <- mydata[ ,list(mac_address = mac_address,
#                          pm25ave =  pm25ave,
#                          total_pm25ave = mean(pm25ave)), 
#                    by = c("UTCDateTime")]
```

Sensors (by mac address) used in this co-location period:
```{r}
print(unique_sensors)
```

```{r, include=FALSE}
#parse sensoravemac data
#sensoravemac$DateTime <- as_datetime(sensoravemac$UTCDateTime,tz="US/Pacific")
```

### split data into groups
```{r, include=FALSE}
#split data into two groups of sensors to plot multiple sensors at once
mydata_split <- split(mydata, f= mydata$mac_address) #splitting into indiv sensors
mydata_s1 <- lapply(mydata_split[1:4],rbind) 
mydata_s1 <- rbindlist(mydata_s1)

mydata_s2 <- lapply(mydata_split[5:7],rbind)
mydata_s2 <- rbindlist(mydata_s2)

# split avg sensoravemac data into groups of sensors (4 or 5)
#sensoravemac_split <- split(sensoravemac, f= sensoravemac$mac_address)
#sensoravemac_s1 <- lapply(sensoravemac_split[1:5],rbind)
#sensoravemac_s1 <- rbindlist(sensoravemac_s1)

#sensoravemac_s2 <- lapply(sensoravemac_split[6:10],rbind)
#sensoravemac_s2 <- rbindlist(sensoravemac_s2)

#sensoravemac_s3 <- lapply(sensoravemac_split[11:14],rbind)
#sensoravemac_s3 <- rbindlist(sensoravemac_s3)
```

---

## PM2.5 Channel Agreement: Individual Sensors for 4/28-5/13

To examine whether the channels agree with each other on individual sensors, I created plots of channel a vs. channel b., and included a regression line and the R^2 value.

### plot regression of channel a vs b
```{r, include=FALSE}
myplots <- lapply(1:length(mydata_split), FUN = function(i){
  ggplot(mydata_split[[i]], aes(x=pm2_5_atm, y=pm2_5_atm_b))+ 
  geom_point(pch=1)+ ggtitle("PM2.5 Channels for 4/28/26 to 5/13/26", subtitle = unique(mydata_split[[i]]$mac_address)) + 
  geom_smooth(method="lm", color="black") +
  theme(plot.title = element_text(hjust = 0.5)) + 
  theme(plot.subtitle = element_text(hjust = 0.5, color="grey32")) +
  xlab("pm2_5_atm (ug/m3)") + ylab("pm2_5_atm_b (ug/m3)") +
  stat_cor(aes(label=after_stat(rr.label))
  #, label.x=5, label.y=8
  )
}) 
```
```{r, fig.show="hold", out.width="50%", warning=FALSE, message=FALSE}
indiv_plots <- lapply(myplots,plot)
```

All the units have R^2 of either 0.95 or 0.96, except unit 5 (F0:24:F9:C6:D7:50), where the R^2 is 0.6 with a large visible difference in the two sensors. While unit 3 (F0:24:F9:C6:6B:D7) had an R^2 =0.95, it had some observations with discrepancies between the two sensors. None of the units seem to have outliers like Cecilia's units did, so I guess this is good? 

### time series of channel a vs b
```{r, include = FALSE}
channel_plots_time_series <- lapply(1:length(mydata_split), FUN = function(i){
  ggplot(mydata_split[[i]]) + 
  geom_point(aes(x = DateTime, y = pm2_5_atm, color = "A")) +
  geom_point(aes(x = DateTime, y = pm2_5_atm_b, color = "B")) +
  ggtitle("PM2.5 per channel from 5/20/26 to 6/1/26", subtitle = unique(mydata_split[[i]]$mac_address)) + 
  xlab("Observation Day") + ylab("PM2.5 Concentration (ug/m3)") +
  scale_x_datetime(date_breaks="2 days") + 
  #scale_color_manual(values=met.brewer("Java")) +
  theme(plot.title = element_text(hjust = 0.5)) +
  theme(plot.subtitle = element_text(hjust = 0.5, color="grey32")) +
  theme(axis.title.y = element_text(vjust = 0.5)) +
  guides(colour = guide_legend(title = "Channel", override.aes = list(size=5,stroke=2,alpha=1)))
}) 
```
``` {r, fig.show="hold", out.width="50%", warning=FALSE, message=FALSE}
indiv_plots <- lapply(channel_plots_time_series,plot)
```


---

## PM2.5 Time Series for Co-Location Period 4/28-5/13

I averaged the data for channels a and b for the colocation period for all sensors. I plotted the time series of the averaged PM2.5 (between channel a and b) for the four groups of sensors here, and inspected them for any outliers and inconsistencies between sensors.

### unit averages plotted for set s1
```{r, include=FALSE}
#(correlation above 0.7) and selection of “best” sensor for those not 
#performing well
#avg time series plots for first set of sensors
pm25_ave_plot_s1 <- ggplot() + 
  ggtitle("Avg. PM2.5 for 4/28/26 to 5/13/26") +
  geom_point(data = mydata_s1, aes(x=DateTime, y=pm25ave, color = as.factor(mac_address)), 
             pch=1, size =0.3, alpha=0.5) +
  xlab("Observation Day") + ylab("PM2.5 Concentration (ug/m3)") +
  scale_x_datetime(date_breaks="2 days") + 
  scale_color_manual(values=met.brewer("Java")) +
  theme(plot.title = element_text(hjust = 0.5)) +
  theme(plot.subtitle = element_text(hjust = 0.5, color="grey32")) +
  theme(axis.title.y = element_text(vjust = 0.5)) +
  guides(colour = guide_legend(title = "Mac address", override.aes = list(size=5,stroke=2,alpha=1)))
```
```{r}
plot(pm25_ave_plot_s1)
```

First four units look good! 

### unit averages plotted for set s2
```{r, include=FALSE}
#avg time series plots for second set of sensors
pm25_ave_plot_s2 <- ggplot() + 
  ggtitle("Avg. PM2.5 for 4/28/26 to 5/13/26") +
  geom_point(data = mydata_s2, aes(x=DateTime, y=pm25ave, color = as.factor(mac_address)), 
             pch=1, size =0.3, alpha=0.5) +
  xlab("Observation Day") + ylab("PM2.5 Concentration (ug/m3)") +
  scale_x_datetime(date_breaks="2 days") + 
  scale_color_manual(values=met.brewer("Java")) +
  theme(plot.title = element_text(hjust = 0.5)) +
  theme(plot.subtitle = element_text(hjust = 0.5, color="grey32")) +
  theme(axis.title.y = element_text(vjust = 0.5)) +
  guides(colour = guide_legend(title = "Mac address",override.aes = list(size=5,stroke=2,alpha=1)))
```
```{r}
plot(pm25_ave_plot_s2)
```

Unit 5 is clearly reading higher than the other two units in that group. 

---

## Average PM2.5 and neph by time

### standardize times, fill missing values, arrange for merging
```{r cal-PA-neph-code-1}
# filter out erroneous measurements
mydata <- mydata %>% filter(pm25ave<500)

#Code from Calibration_PA_Neph.R in Healthy Schools
newdatetime <- seq(floor_date(min(mydata$DateTime), "2 min"),
                   ceiling_date(max(mydata$DateTime)), by = "2 min")
newdatetime <- setDT(data.frame(DateTime = newdatetime))

mydata_list <- split(mydata, by = "mac_address")

mydata_1min_list <- lapply(mydata_list, FUN = function(x){
  
 test <- rbindlist(list(x, newdatetime), fill = T)
 setkey(test, DateTime)
 
 colvals = c("mac_address","firmware_ver","hardware")
 
 test[, (colvals) := lapply(.SD, FUN = function(i) {unique(i)[2]}), 
      .SDcols = colvals]
 
 colvals = colnames(x)[sapply(x, is.numeric)]
 
 test[, (colvals) := lapply(.SD, FUN = function(i){ 
   na.approx(i, na.rm=F)}), 
      .SDcols = colvals]
 
 test = test[!is.na(`p_2_5_um` ), ]
 
 test
})

mydata_1min <- rbindlist(mydata_1min_list)
neph <- rbindlist(all_neph[1])

setkey(mydata_1min, DateTime)
setkey(neph, DateTime)

mydata_1min <- neph[mydata_1min]
```

### regression on neph and PA data
```{r lm-sensors1}
lmval <- lm(data = mydata_1min, npm25_LFP ~ pm25ave + current_humidity)
summary(lmval)
```

## Unit vs. Total Average PM2.5 for 4/28/26 to 5/13/26

### plot regression of unit average vs all units average
```{r}
#create dt with time averaged PM2.5 & NPM2.5, rel humidity, mac address, and avg. PM2.5 per sensor
mydata_1min_timeavg <- mydata_1min[ , list(timeavePM25 =  mean(pm25ave),
                          timeaveNPM25 = mean(npm25_LFP),
                          rel_humidity = current_humidity,
                          mac_address=mac_address,
                          pm25ave),
                    by = c("DateTime")]
#filter the NAs out
mydata_1min_timeavg <- mydata_1min_timeavg %>% filter(is.na(timeaveNPM25)==FALSE)

#split dt into each sensor
mydata_1minave_split <- split(mydata_1min_timeavg, mydata_1min_timeavg$mac_address)

#plot individual sensor against average
myplots <- lapply(1:length(mydata_1minave_split), FUN = function(i){
  ggplot(mydata_1minave_split[[i]], aes(x=timeavePM25, y=pm25ave))+ 
  geom_point(pch=1)+ ggtitle("Sensor PM2.5 Compared to All Co-Located Sensors for 4/28 to 5/13",
          subtitle = unique(mydata_1minave_split[[i]]$mac_address)) + 
  geom_smooth(method="lm", color="black") +
  theme(plot.title = element_text(hjust = 0.5)) + 
  theme(plot.subtitle = element_text(hjust = 0.5, color="grey32")) +
  xlab("Total PM2.5 average (ug/m3)") + ylab("Individual Sensor PM2.5 (ug/m3)") +
  stat_cor(aes(label=after_stat(rr.label))
  #, label.x=7, label.y=7
  )
})
```
```{r, fig.show="hold", out.width="50%", warning=FALSE, message=FALSE}
indiv_plots <- lapply(myplots,plot)
```

---

## Comparing the nephelometer to PA data 4/28 - 5/13

### plot neph vs PA averages 
```{r}
mydata <- mydata %>% filter(pm25ave<500)

#Correct one
pm25_neph_428_513 <- ggplot() + 
  ggtitle("Avg. PM2.5 for 4/28/26 to 5/13/26", subtitle = "Nephelometer (green) and PA (pink)") +
  geom_point(data = mydata, aes(x=DateTime, y=pm25ave), 
             pch=1, size =0.5, color="magenta", alpha=0.15) +
  geom_point(data = all_neph[[1]], aes(x=DateTime, y=npm25_LFP), 
            pch=2, size =0.5, color="limegreen") +
  xlab("Observation Day") + ylab("PM2.5 Concentration (ug/m3)") +
  scale_x_datetime(date_breaks="1 day") + 
  theme(plot.title = element_text(hjust = 0.5)) +
  theme(plot.subtitle = element_text(hjust = 0.5, color="grey32")) +
  theme(axis.title.y = element_text(vjust = 0.5)) +
  theme(legend.position = "right")

plot(pm25_neph_428_513)
```

# 5/13/26 - 5/20/2026 Co-Location

## Load and process PA files

### load 5/13 - 5/20 files
```{r, message=FALSE, warning=FALSE}
# List of CSV files that we want from this folder (CHANGE THIS PER FOLDER)
all_files <- list.files(here(), recursive = TRUE)
csv_files <- all_files[grepl("^CoLo2_13May-20May/.*/.*\\.csv$", all_files)]
unique_sensors <- unique(get_sensor_name(csv_files))

#merge all the data for selected colocation period
mydatalist <- lapply(1:length(csv_files), FUN = function(i){
  read_and_name_csv(csv_files[i])
})
mydata <- rbindlist(mydatalist)

#parse date/time
mydata$DateTime <- as_datetime(mydata$UTCDateTime,tz="US/Pacific")
```

### process chanel averages
```{r,include=FALSE}
# average channel a and channel b
mydata[, pm25ave := rowMeans(.SD), 
       by = c("mac_address", "UTCDateTime"), 
       .SDcols = c("pm2_5_atm","pm2_5_atm_b") ]

# create separate table that is just week avg & sd data, mac address
myavemac <- mydata[ ,list(weekavepm25 =  mean(pm25ave),
                          weeksdpm25 = sd(pm25ave) ), 
                    by = c("mac_address")]

#average PM2.5 data over time -- TO-DO, THE BELOW DIDN'T WORK
#sensoravemac <- mydata[ ,list(mac_address = mac_address,
#                          pm25ave =  pm25ave,
#                          total_pm25ave = mean(pm25ave)), 
#                    by = c("UTCDateTime")]
```

Sensors (by mac address) used in this co-location period:
```{r}
print(unique_sensors)
```

```{r, include=FALSE}
#parse sensoravemac data
#sensoravemac$DateTime <- as_datetime(sensoravemac$UTCDateTime,tz="US/Pacific")
```

### split data into groups
```{r, include=FALSE}
#split data into two groups of sensors to plot multiple sensors at once
mydata_split <- split(mydata, f= mydata$mac_address) #splitting into indiv sensors
mydata_s1 <- lapply(mydata_split[1:4],rbind) 
mydata_s1 <- rbindlist(mydata_s1)

mydata_s2 <- lapply(mydata_split[5:9],rbind)
mydata_s2 <- rbindlist(mydata_s2)

# split avg sensoravemac data into groups of sensors (4 or 5)
#sensoravemac_split <- split(sensoravemac, f= sensoravemac$mac_address)
#sensoravemac_s1 <- lapply(sensoravemac_split[1:5],rbind)
#sensoravemac_s1 <- rbindlist(sensoravemac_s1)

#sensoravemac_s2 <- lapply(sensoravemac_split[6:10],rbind)
#sensoravemac_s2 <- rbindlist(sensoravemac_s2)

#sensoravemac_s3 <- lapply(sensoravemac_split[11:14],rbind)
#sensoravemac_s3 <- rbindlist(sensoravemac_s3)
```

---

## PM2.5 Channel Agreement: Individual Sensors for 5/13-5/20

To examine whether the channels agree with each other on individual sensors, I created plots of channel a vs. channel b., and included a regression line and the R^2 value.

### plot regression of channel a vs b
```{r, include=FALSE}
myplots <- lapply(1:length(mydata_split), FUN = function(i){
  ggplot(mydata_split[[i]], aes(x=pm2_5_atm, y=pm2_5_atm_b))+ 
  geom_point(pch=1)+ ggtitle("PM2.5 Channels for 5/13/26 to 5/20/26", subtitle = unique(mydata_split[[i]]$mac_address)) + 
  geom_smooth(method="lm", color="black") +
  theme(plot.title = element_text(hjust = 0.5)) + 
  theme(plot.subtitle = element_text(hjust = 0.5, color="grey32")) +
  xlab("pm2_5_atm (ug/m3)") + ylab("pm2_5_atm_b (ug/m3)") +
  stat_cor(aes(label=after_stat(rr.label))
  #, label.x=5, label.y=8
  )
}) 
```
``` {r, include=FALSE, echo=FALSE}
indiv_plots <- lapply(myplots,plot)
```

All the units have R^2 from 0.95 to 0.97, except unit 9 (F0_24_F9_C6_C7_8F), where the R^2 is 0.0075. This appears to be due to two high outliers on one of the sensors - let's try filtering those out and see if that fixes things. 

### filter out outliers for bad sensors, rerun plots
```{r, include=FALSE}
### Cecilia example for what she did for a bad unit
mydata_split[[9]] <- mydata_split[[9]] %>% filter(pm2_5_atm<500)
mydata_split[[9]] <- mydata_split[[9]] %>% filter(pm2_5_atm_b<500)


#Re-run plots
myplots <- lapply(1:length(mydata_split), FUN = function(i){
  ggplot(mydata_split[[i]], aes(x=pm2_5_atm, y=pm2_5_atm_b))+ 
  geom_point(pch=1)+ ggtitle("PM2.5 Channels for 5/13/26 to 5/20/26", subtitle = unique(mydata_split[[i]]$mac_address)) + 
  geom_smooth(method="lm", color="black") +
  theme(plot.title = element_text(hjust = 0.5)) + 
  theme(plot.subtitle = element_text(hjust = 0.5, color="grey32")) +
  xlab("pm2_5_atm (ug/m3)") + ylab("pm2_5_atm_b (ug/m3)") +
  stat_cor(aes(label=after_stat(rr.label)), label.x=25, label.y=8)
})
```
```{r, fig.show="hold", out.width="50%", warning=FALSE, message=FALSE}
indiv_plots <- lapply(myplots,plot)
```

This fixes things right up, with unit 9 now having a R^2 of 0.96. Looking good! 

```{r, include= FALSE}
#let's remake the s1 and s2 groups now that we've filtered out those outliers. 
mydata_s1 <- lapply(mydata_split[1:4],rbind) 
mydata_s1 <- rbindlist(mydata_s1)

mydata_s2 <- lapply(mydata_split[5:9],rbind)
mydata_s2 <- rbindlist(mydata_s2)
```

---

## PM2.5 Time Series for Co-Location Period 5/13-5/20

I averaged the data for channels a and b for the colocation period for all sensors. I plotted the time series of the averaged PM2.5 (between channel a and b) for the four groups of sensors here, and inspected them for any outliers and inconsistencies between sensors.

### unit averages plotted for set s1
```{r, include=FALSE}
#(correlation above 0.7) and selection of “best” sensor for those not 
#performing well
#avg time series plots for first set of sensors
pm25_ave_plot_s1 <- ggplot() + 
  ggtitle("Avg. PM2.5 for 5/13/26 to 5/20/26") +
  geom_point(data = mydata_s1, aes(x=DateTime, y=pm25ave, color = as.factor(mac_address)), 
             pch=1, size =0.3, alpha=0.5) +
  xlab("Observation Day") + ylab("PM2.5 Concentration (ug/m3)") +
  scale_x_datetime(date_breaks="2 days") + 
  scale_color_manual(values=met.brewer("Java")) +
  theme(plot.title = element_text(hjust = 0.5)) +
  theme(plot.subtitle = element_text(hjust = 0.5, color="grey32")) +
  theme(axis.title.y = element_text(vjust = 0.5)) +
  guides(colour = guide_legend(title = "Mac address", override.aes = list(size=5,stroke=2,alpha=1)))
```
```{r}
plot(pm25_ave_plot_s1)
```

First four units look good! It looks like there were some times where 4b:b8 were on while the others weren't - maybe a power failure on a specific outlet? 

### unit averages plotted for set s2
```{r, include=FALSE}
#avg time series plots for second set of sensors
pm25_ave_plot_s2 <- ggplot() + 
  ggtitle("Avg. PM2.5 for 5/13/26 to 5/20/26") +
  geom_point(data = mydata_s2, aes(x=DateTime, y=pm25ave, color = as.factor(mac_address)), 
             pch=1, size =0.3, alpha=0.5) +
  xlab("Observation Day") + ylab("PM2.5 Concentration (ug/m3)") +
  scale_x_datetime(date_breaks="2 days") + 
  scale_color_manual(values=met.brewer("Java")) +
  theme(plot.title = element_text(hjust = 0.5)) +
  theme(plot.subtitle = element_text(hjust = 0.5, color="grey32")) +
  theme(axis.title.y = element_text(vjust = 0.5)) +
  guides(colour = guide_legend(title = "Mac address",override.aes = list(size=5,stroke=2,alpha=1)))
```
```{r}
plot(pm25_ave_plot_s2)
```

Looks good, some similarly missing data for some units. Not sure what happened there. 

---

## Average PM2.5 and neph by time

### standardize times, fill missing values, arrange for merging
```{r cal-PA-neph-code-2}
# filter out erroneous measurements
mydata <- mydata %>% filter(pm25ave<300)

#Code from Calibration_PA_Neph.R in Healthy Schools
newdatetime <- seq(floor_date(min(mydata$DateTime), "2 min"),
                   ceiling_date(max(mydata$DateTime)), by = "2 min")
newdatetime <- setDT(data.frame(DateTime = newdatetime))

mydata_list <- split(mydata, by = "mac_address")

mydata_1min_list <- lapply(mydata_list, FUN = function(x){
  
 test <- rbindlist(list(x, newdatetime), fill = T)
 setkey(test, DateTime)
 
 colvals = c("mac_address","firmware_ver","hardware")
 
 test[, (colvals) := lapply(.SD, FUN = function(i) {unique(i)[2]}), 
      .SDcols = colvals]
 
 colvals = colnames(x)[sapply(x, is.numeric)]
 
 test[, (colvals) := lapply(.SD, FUN = function(i){ 
   na.approx(i, na.rm=F)}), 
      .SDcols = colvals]
 
 test = test[!is.na(`p_2_5_um` ), ]
 
 test
})

mydata_1min <- rbindlist(mydata_1min_list)
neph <- rbindlist(all_neph[2])

setkey(mydata_1min, DateTime)
setkey(neph, DateTime)

mydata_1min <- neph[mydata_1min]
```

### regression on neph and PA data
```{r lm-sensors2}
lmval <- lm(data = mydata_1min, npm25_LFP ~ pm25ave + current_humidity)
summary(lmval)
```

## Unit vs. Total Average PM2.5 for 5/13/26 to 5/20/26

### plot regression of unit average vs all units average
```{r}
#create dt with time averaged PM2.5 & NPM2.5, rel humidity, mac address, and avg. PM2.5 per sensor
mydata_1min_timeavg <- mydata_1min[ , list(timeavePM25 =  mean(pm25ave),
                          timeaveNPM25 = mean(npm25_LFP),
                          rel_humidity = current_humidity,
                          mac_address=mac_address,
                          pm25ave),
                    by = c("DateTime")]
#filter the NAs out
mydata_1min_timeavg <- mydata_1min_timeavg %>% filter(is.na(timeaveNPM25)==FALSE)

#split dt into each sensor
mydata_1minave_split <- split(mydata_1min_timeavg, mydata_1min_timeavg$mac_address)

#plot individual sensor against average
myplots <- lapply(1:length(mydata_1minave_split), FUN = function(i){
  ggplot(mydata_1minave_split[[i]], aes(x=timeavePM25, y=pm25ave))+ 
  geom_point(pch=1)+ ggtitle("Sensor PM2.5 Compared to All Co-Located Sensors for 5/13 to 5/20",
          subtitle = unique(mydata_1minave_split[[i]]$mac_address)) + 
  geom_smooth(method="lm", color="black") +
  theme(plot.title = element_text(hjust = 0.5)) + 
  theme(plot.subtitle = element_text(hjust = 0.5, color="grey32")) +
  xlab("Total PM2.5 average (ug/m3)") + ylab("Individual Sensor PM2.5 (ug/m3)") +
  stat_cor(aes(label=after_stat(rr.label))
  #, label.x=7, label.y=7
  )
})
```
```{r, fig.show="hold", out.width="50%", warning=FALSE, message=FALSE}
indiv_plots <- lapply(myplots,plot)
```

---

## Comparing the nephelometer to PA data 5/13 - 5/20

### plot neph vs PA averages 
```{r}

mydata <- mydata %>% filter(pm25ave<500)

#Correct one
pm25_neph_513_520 <- ggplot() + 
  ggtitle("Avg. PM2.5 for 5/13/26 to 5/20/26", subtitle = "Nephelometer (green) and PA (pink)") +
  geom_point(data = mydata, aes(x=DateTime, y=pm25ave), 
             pch=1, size =0.5, color="magenta", alpha=0.15) +
  geom_point(data = all_neph[[2]], aes(x=DateTime, y=npm25_LFP), 
            pch=2, size =0.5, color="limegreen") +
  xlab("Observation Day") + ylab("PM2.5 Concentration (ug/m3)") +
  scale_x_datetime(date_breaks="4 day") + 
  theme(plot.title = element_text(hjust = 0.5)) +
  theme(plot.subtitle = element_text(hjust = 0.5, color="grey32")) +
  theme(axis.title.y = element_text(vjust = 0.5)) +
  theme(legend.position = "right")

plot(pm25_neph_513_520) 
```

# 5/20/26 - 6/01/2026 Co-Location

## Load and process PA files

### load 5/20 - 6/1 files
```{r, message=FALSE, warning=FALSE}
# List of CSV files that we want from this folder (CHANGE THIS PER FOLDER)
all_files <- list.files(here(), recursive = TRUE)
csv_files <- all_files[grepl("^CoLo3_20May-1Jun/.*/.*\\.csv$", all_files)]
unique_sensors <- unique(get_sensor_name(csv_files))

#merge all the data for selected colocation period
mydatalist <- lapply(1:length(csv_files), FUN = function(i){
  read_and_name_csv(csv_files[i])
})
mydata <- rbindlist(mydatalist)

#parse date/time
mydata$DateTime <- as_datetime(mydata$UTCDateTime,tz="US/Pacific")
```

### process chanel averages
```{r,include=FALSE}
# average channel a and channel b
mydata[, pm25ave := rowMeans(.SD), 
       by = c("mac_address", "UTCDateTime"), 
       .SDcols = c("pm2_5_atm","pm2_5_atm_b") ]

# create separate table that is just week avg & sd data, mac address
myavemac <- mydata[ ,list(weekavepm25 =  mean(pm25ave),
                          weeksdpm25 = sd(pm25ave) ), 
                    by = c("mac_address")]

#average PM2.5 data over time -- TO-DO, THE BELOW DIDN'T WORK
#sensoravemac <- mydata[ ,list(mac_address = mac_address,
#                          pm25ave =  pm25ave,
#                          total_pm25ave = mean(pm25ave)), 
#                    by = c("UTCDateTime")]
```

Sensors (by mac address) used in this co-location period:
```{r}
print(unique_sensors)
```

```{r, include=FALSE}
#parse sensoravemac data
#sensoravemac$DateTime <- as_datetime(sensoravemac$UTCDateTime,tz="US/Pacific")
```

### split data into groups
```{r, include=FALSE}
#split data into two groups of sensors to plot multiple sensors at once
mydata_split <- split(mydata, f= mydata$mac_address) #splitting into indiv sensors
mydata_s1 <- lapply(mydata_split[1:5],rbind)
mydata_s1 <- rbindlist(mydata_s1)

mydata_s2 <- lapply(mydata_split[6:10],rbind)
mydata_s2 <- rbindlist(mydata_s2)

# split avg sensoravemac data into groups of sensors (4 or 5)
#sensoravemac_split <- split(sensoravemac, f= sensoravemac$mac_address)
#sensoravemac_s1 <- lapply(sensoravemac_split[1:5],rbind)
#sensoravemac_s1 <- rbindlist(sensoravemac_s1)

#sensoravemac_s2 <- lapply(sensoravemac_split[6:10],rbind)
#sensoravemac_s2 <- rbindlist(sensoravemac_s2)

#sensoravemac_s3 <- lapply(sensoravemac_split[11:14],rbind)
#sensoravemac_s3 <- rbindlist(sensoravemac_s3)
```

---

## PM2.5 Channel Agreement: Individual Sensors for 5/20-6/1

To examine whether the channels agree with each other on individual sensors, I created plots of channel a vs. channel b., and included a regression line and the R^2 value.

### plot regression of channel a vs b
```{r, include=FALSE}
myplots <- lapply(1:length(mydata_split), FUN = function(i){
  ggplot(mydata_split[[i]], aes(x=pm2_5_atm, y=pm2_5_atm_b))+ 
  geom_point(pch=1)+ ggtitle("PM2.5 Channels for 5/20/26 to 6/1/26", subtitle = unique(mydata_split[[i]]$mac_address)) + 
  geom_smooth(method="lm", color="black") +
  theme(plot.title = element_text(hjust = 0.5)) + 
  theme(plot.subtitle = element_text(hjust = 0.5, color="grey32")) +
  xlab("pm2_5_atm (ug/m3)") + ylab("pm2_5_atm_b (ug/m3)") +
  stat_cor(aes(label=after_stat(rr.label))
  #, label.x=5, label.y=8
  )
}) 
```
``` {r, fig.show="hold", out.width="50%", warning=FALSE, message=FALSE}
indiv_plots <- lapply(myplots,plot)
```

Wow, more issues on this batch than typical. Unit f0:24:f9:c6:91:c0 has an R^2 of 0.59, it looks like many of the points are along a good trend, so I'm interested in looking at a time series of the readings and see if one sensor went bad at a certain point through the colocation. 

Next problematic unit is f0:24:f9:c6:c8:85, which has about 166 readings on sensor b that are well over 250ug/m3, with many nearing 3500 ug/m3. This was a string of bad readings from 5/23 at 0601 to 1126. Even if we filter out all readings over 250ug/m3, we get an R^2 of 0.59, so definetely some big issues there. 

```{r, fig.show="hold", out.width="50%", warning=FALSE, message=FALSE}
f0_24_f9_c6_c8_85_high <- mydata |> 
  filter(mac_address == "f0:24:f9:c6:c8:85") |> 
  filter(pm2_5_atm_b > 250)

f0_24_f9_c6_c8_85_low <- mydata |> 
  filter(mac_address == "f0:24:f9:c6:c8:85") |> 
  filter(pm2_5_atm_b < 250)

ggplot(f0_24_f9_c6_c8_85_low, aes(x=pm2_5_atm, y=pm2_5_atm_b))+ 
  geom_point(pch=1)+ ggtitle("PM2.5 Channels for 5/20/26 to 6/1/26, >250um/m3 filtered out", subtitle = unique(f0_24_f9_c6_c8_85_low$mac_address)) + 
  geom_smooth(method="lm", color="black") +
  theme(plot.title = element_text(hjust = 0.5)) + 
  theme(plot.subtitle = element_text(hjust = 0.5, color="grey32")) +
  xlab("pm2_5_atm (ug/m3)") + ylab("pm2_5_atm_b (ug/m3)") +
  stat_cor(aes(label=after_stat(rr.label))
  #, label.x=5, label.y=8
  )
```

Unit f0:24:f9:c6:e4:9e has an R^2 of 0.9, which is lower than typical, and some visible deviations from the A channel. These deviations center around 5/23 at 0526, which is about a half hour before one of the channels on a different unit went off the rails... interesting. EXCLUDE THIS TIME PERIOD AND RERUN??

Otherwise, the 8 remaining units have R^2 from 0.9 to 0.96, with many of them tending to be more around the 0.92 range. Not the best, but they should be fine. 

### time series of channel a vs b
```{r, include = FALSE}
channel_plots_time_series <- lapply(1:length(mydata_split), FUN = function(i){
  ggplot(mydata_split[[i]]) + 
  geom_point(aes(x = DateTime, y = pm2_5_atm, color = "A")) +
  geom_point(aes(x = DateTime, y = pm2_5_atm_b, color = "B")) +
  ggtitle("PM2.5 per channel from 5/20/26 to 6/1/26", subtitle = unique(mydata_split[[i]]$mac_address)) + 
  xlab("Observation Day") + ylab("PM2.5 Concentration (ug/m3)") +
  scale_x_datetime(date_breaks="2 days") + 
  #scale_color_manual(values=met.brewer("Java")) +
  theme(plot.title = element_text(hjust = 0.5)) +
  theme(plot.subtitle = element_text(hjust = 0.5, color="grey32")) +
  theme(axis.title.y = element_text(vjust = 0.5)) +
  guides(colour = guide_legend(title = "Channel", override.aes = list(size=5,stroke=2,alpha=1)))
}) 
```
``` {r, fig.show="hold", out.width="50%", warning=FALSE, message=FALSE}
indiv_plots <- lapply(channel_plots_time_series,plot)
```

Looking at unit f0:24:f9:c6:91:c0, it does look like after 5/23 at about 0600 it started having massive random spikes on channel A, while otherwise being mostly well correlated. With these spikes happening at more or less random, I don't think it can be reliably used. 

``` {r, fig.show="hold", out.width="50%", warning=FALSE, message=FALSE}
ggplot(f0_24_f9_c6_c8_85_low) + 
  geom_point(aes(x = DateTime, y = pm2_5_atm, color = "A")) +
  geom_point(aes(x = DateTime, y = pm2_5_atm_b, color = "B")) +
  ggtitle("PM2.5 per channel from 5/20/26 to 6/1/26, >250um/m3 filtered out", subtitle = unique(f0_24_f9_c6_c8_85_low$mac_address)) + 
  xlab("Observation Day") + ylab("PM2.5 Concentration (ug/m3)") +
  scale_x_datetime(date_breaks="2 days") + 
  #scale_color_manual(values=met.brewer("Java")) +
  theme(plot.title = element_text(hjust = 0.5)) +
  theme(plot.subtitle = element_text(hjust = 0.5, color="grey32")) +
  theme(axis.title.y = element_text(vjust = 0.5)) +
  guides(colour = guide_legend(title = "Channel", override.aes = list(size=5,stroke=2,alpha=1)))
```

Here's also an additional time series for the unit with crazy high readings, but with those filtered out. Still looking like the A channel is having some issues. 

### Reconstruction of sets with defective units removed
```{r, include = FALSE}
mydata_s1 <- lapply(mydata_split[c(1, 2, 3, 5)],rbind)
mydata_s1 <- rbindlist(mydata_s1)

mydata_s2 <- lapply(mydata_split[7:10],rbind)
mydata_s2 <- rbindlist(mydata_s2)
```

---

## PM2.5 Time Series for Co-Location Period 5/20-6/1

I averaged the data for channels a and b for the colocation period for all viable sensors. I plotted the time series of the averaged PM2.5 (between channel a and b) for the groups of sensors here, and inspected them for any outliers and inconsistencies between sensors.

### unit averages plotted for set s1
```{r, include=FALSE}
#(correlation above 0.7) and selection of “best” sensor for those not 
#performing well
#avg time series plots for first set of sensors
pm25_ave_plot_s1 <- ggplot() + 
  ggtitle("Avg. PM2.5 for 5/20/26 to 6/1/26") +
  geom_point(data = mydata_s1, aes(x=DateTime, y=pm25ave, color = as.factor(mac_address)), 
             pch=1, size =0.3, alpha=0.5) +
  xlab("Observation Day") + ylab("PM2.5 Concentration (ug/m3)") +
  scale_x_datetime(date_breaks="2 days") + 
  scale_color_manual(values=met.brewer("Java")) +
  theme(plot.title = element_text(hjust = 0.5)) +
  theme(plot.subtitle = element_text(hjust = 0.5, color="grey32")) +
  theme(axis.title.y = element_text(vjust = 0.5)) +
  guides(colour = guide_legend(title = "Mac address", override.aes = list(size=5,stroke=2,alpha=1)))
```
```{r}
plot(pm25_ave_plot_s1)
```


### unit averages plotted for set s2
```{r, include=FALSE}
#avg time series plots for second set of sensors
pm25_ave_plot_s2 <- ggplot() + 
  ggtitle("Avg. PM2.5 for 5/20/26 to 6/1/26") +
  geom_point(data = mydata_s2, aes(x=DateTime, y=pm25ave, color = as.factor(mac_address)), 
             pch=1, size =0.3, alpha=0.5) +
  xlab("Observation Day") + ylab("PM2.5 Concentration (ug/m3)") +
  scale_x_datetime(date_breaks="2 days") + 
  scale_color_manual(values=met.brewer("Java")) +
  theme(plot.title = element_text(hjust = 0.5)) +
  theme(plot.subtitle = element_text(hjust = 0.5, color="grey32")) +
  theme(axis.title.y = element_text(vjust = 0.5)) +
  guides(colour = guide_legend(title = "Mac address",override.aes = list(size=5,stroke=2,alpha=1)))
```
```{r}
plot(pm25_ave_plot_s2)
```

---

## Average PM2.5 and neph by time

### standardize times, fill missing values, arrange for merging
```{r cal-PA-neph-code-3}

#Code from Calibration_PA_Neph.R in Healthy Schools
newdatetime <- seq(floor_date(min(mydata$DateTime), "2 min"),
                   ceiling_date(max(mydata$DateTime)), by = "2 min")
newdatetime <- setDT(data.frame(DateTime = newdatetime))

mydata_list <- split(mydata, by = "mac_address")

mydata_1min_list <- lapply(mydata_list, FUN = function(x){
  
 test <- rbindlist(list(x, newdatetime), fill = T)
 setkey(test, DateTime)
 
 colvals = c("mac_address","firmware_ver","hardware")
 
 test[, (colvals) := lapply(.SD, FUN = function(i) {unique(i)[2]}), 
      .SDcols = colvals]
 
 colvals = colnames(x)[sapply(x, is.numeric)]
 
 test[, (colvals) := lapply(.SD, FUN = function(i){ 
   na.approx(i, na.rm=F)}), 
      .SDcols = colvals]
 
 test = test[!is.na(`p_2_5_um` ), ]
 
 test
})

mydata_1min <- rbindlist(mydata_1min_list[c(1:3, 5, 7:10)])
neph <- rbindlist(all_neph[3])

setkey(mydata_1min, DateTime)
setkey(neph, DateTime)

mydata_1min <- neph[mydata_1min]
```

### regression on neph and PA data
```{r lm-sensors3}
lmval <- lm(data = mydata_1min, npm25_LFP ~ pm25ave + current_humidity)
summary(lmval)
```

## Unit vs. Total Average PM2.5 for 5/20/26 to 6/1/26

### plot regression of unit average vs all units average
```{r}
#create dt with time averaged PM2.5 & NPM2.5, rel humidity, mac address, and avg. PM2.5 per sensor
mydata_1min_timeavg <- mydata_1min[ , list(timeavePM25 =  mean(pm25ave),
                          timeaveNPM25 = mean(npm25_LFP),
                          rel_humidity = current_humidity,
                          mac_address=mac_address,
                          pm25ave),
                    by = c("DateTime")]
#filter the NAs out
mydata_1min_timeavg <- mydata_1min_timeavg %>% filter(is.na(timeaveNPM25)==FALSE)

#split dt into each sensor
mydata_1minave_split <- split(mydata_1min_timeavg, mydata_1min_timeavg$mac_address)

#plot individual sensor against average
myplots <- lapply(1:length(mydata_1minave_split), FUN = function(i){
  ggplot(mydata_1minave_split[[i]], aes(x=timeavePM25, y=pm25ave))+ 
  geom_point(pch=1)+ ggtitle("Sensor PM2.5 Compared to Well-Performing Co-Located Sensors for 5/20 to 6/1",
          subtitle = unique(mydata_1minave_split[[i]]$mac_address)) + 
  geom_smooth(method="lm", color="black") +
  theme(plot.title = element_text(hjust = 0.5)) + 
  theme(plot.subtitle = element_text(hjust = 0.5, color="grey32")) +
  xlab("Total PM2.5 average (ug/m3)") + ylab("Individual Sensor PM2.5 (ug/m3)") +
  stat_cor(aes(label=after_stat(rr.label))
  #, label.x=7, label.y=7
  )
})
```
```{r, fig.show="hold", out.width="50%", warning=FALSE, message=FALSE}
indiv_plots <- lapply(myplots,plot)
```

---

## Comparing the nephelometer to PA data 5/20 - 6/1

### plot neph vs PA averages 
```{r}

mydata <- mydata %>% filter(pm25ave<500)

#Correct one
pm25_neph_513_520 <- ggplot() + 
  ggtitle("Avg. PM2.5 for 5/20/26 to 6/1/26", subtitle = "Nephelometer (green) and PA (pink)") +
  geom_point(data = mydata_1min, aes(x=DateTime, y=pm25ave), 
             pch=1, size =0.5, color="magenta", alpha=0.15) +
  geom_point(data = all_neph[[3]], aes(x=DateTime, y=npm25_LFP), 
            pch=2, size =0.5, color="limegreen") +
  xlab("Observation Day") + ylab("PM2.5 Concentration (ug/m3)") +
  scale_x_datetime(date_breaks="4 day") + 
  theme(plot.title = element_text(hjust = 0.5)) +
  theme(plot.subtitle = element_text(hjust = 0.5, color="grey32")) +
  theme(axis.title.y = element_text(vjust = 0.5)) +
  theme(legend.position = "right")

plot(pm25_neph_513_520) 
```

# Troubleshooting Location (lo4)

## Load and process PA files

### load lo4 files
```{r, message=FALSE, warning=FALSE}
# List of CSV files that we want from this folder (CHANGE THIS PER FOLDER)
all_files <- list.files(here(), recursive = TRUE)
csv_files <- all_files[grepl("^Lo4/.*/.*\\.csv$", all_files)]
unique_sensors <- unique(get_sensor_name(csv_files))

#merge all the data for selected colocation period
mydatalist <- lapply(1:length(csv_files), FUN = function(i){
  read_and_name_csv(csv_files[i])
})
mydata <- rbindlist(mydatalist)

#parse date/time
mydata$DateTime <- as_datetime(mydata$UTCDateTime,tz="US/Pacific")
```

### process chanel averages
```{r,include=FALSE}
# average channel a and channel b
mydata[, pm25ave := rowMeans(.SD), 
       by = c("mac_address", "UTCDateTime"), 
       .SDcols = c("pm2_5_atm","pm2_5_atm_b") ]

# create separate table that is just week avg & sd data, mac address
myavemac <- mydata[ ,list(weekavepm25 =  mean(pm25ave),
                          weeksdpm25 = sd(pm25ave) ), 
                    by = c("mac_address")]

#average PM2.5 data over time -- TO-DO, THE BELOW DIDN'T WORK
#sensoravemac <- mydata[ ,list(mac_address = mac_address,
#                          pm25ave =  pm25ave,
#                          total_pm25ave = mean(pm25ave)), 
#                    by = c("UTCDateTime")]
```

Sensors (by mac address) used in this co-location period:
```{r}
print(unique_sensors)
```

```{r, include=FALSE}
#parse sensoravemac data
#sensoravemac$DateTime <- as_datetime(sensoravemac$UTCDateTime,tz="US/Pacific")
```

### split data into groups
```{r, include=FALSE}
#split data into two groups of sensors to plot multiple sensors at once
mydata_split <- split(mydata, f= mydata$mac_address) #splitting into indiv sensors
mydata_s1 <- lapply(mydata_split[1:2],rbind)
mydata_s1 <- rbindlist(mydata_s1)

# split avg sensoravemac data into groups of sensors (4 or 5)
#sensoravemac_split <- split(sensoravemac, f= sensoravemac$mac_address)
#sensoravemac_s1 <- lapply(sensoravemac_split[1:5],rbind)
#sensoravemac_s1 <- rbindlist(sensoravemac_s1)

#sensoravemac_s2 <- lapply(sensoravemac_split[6:10],rbind)
#sensoravemac_s2 <- rbindlist(sensoravemac_s2)

#sensoravemac_s3 <- lapply(sensoravemac_split[11:14],rbind)
#sensoravemac_s3 <- rbindlist(sensoravemac_s3)
```

---

## PM2.5 Channel Agreement: Individual Sensors for 5/20-6/1

To examine whether the channels agree with each other on individual sensors, I created plots of channel a vs. channel b., and included a regression line and the R^2 value.

### plot regression of channel a vs b
```{r, include=FALSE}
myplots <- lapply(1:length(mydata_split), FUN = function(i){
  ggplot(mydata_split[[i]], aes(x=pm2_5_atm, y=pm2_5_atm_b))+ 
  geom_point(pch=1)+ ggtitle("PM2.5 Channels for lo4", subtitle = unique(mydata_split[[i]]$mac_address)) + 
  geom_smooth(method="lm", color="black") +
  theme(plot.title = element_text(hjust = 0.5)) + 
  theme(plot.subtitle = element_text(hjust = 0.5, color="grey32")) +
  xlab("pm2_5_atm (ug/m3)") + ylab("pm2_5_atm_b (ug/m3)") +
  stat_cor(aes(label=after_stat(rr.label))
  #, label.x=5, label.y=8
  )
}) 
```
``` {r, fig.show="hold", out.width="50%", warning=FALSE, message=FALSE}
indiv_plots <- lapply(myplots,plot)
```

commentary or whatever

```{r, fig.show="hold", out.width="50%", warning=FALSE, message=FALSE}
f0_24_f9_c6_c8_85_high <- mydata |> 
  filter(mac_address == "f0:24:f9:c6:c8:85") |> 
  filter(pm2_5_atm > 250)

f0_24_f9_c6_c8_85_low <- mydata |> 
  filter(mac_address == "f0:24:f9:c6:c8:85") |> 
  filter(pm2_5_atm < 250)

ggplot(f0_24_f9_c6_c8_85_low, aes(x=pm2_5_atm, y=pm2_5_atm_b))+ 
  geom_point(pch=1)+ ggtitle("PM2.5 Channels for 5/20/26 to 6/1/26, >250um/m3 filtered out", subtitle = unique(f0_24_f9_c6_c8_85_low$mac_address)) + 
  geom_smooth(method="lm", color="black") +
  theme(plot.title = element_text(hjust = 0.5)) + 
  theme(plot.subtitle = element_text(hjust = 0.5, color="grey32")) +
  xlab("pm2_5_atm (ug/m3)") + ylab("pm2_5_atm_b (ug/m3)") +
  stat_cor(aes(label=after_stat(rr.label))
  #, label.x=5, label.y=8
  )
```



### time series of channel a vs b
```{r, include = FALSE}
channel_plots_time_series <- lapply(1:length(mydata_split), FUN = function(i){
  ggplot(mydata_split[[i]]) + 
  geom_point(aes(x = DateTime, y = pm2_5_atm, color = "A")) +
  geom_point(aes(x = DateTime, y = pm2_5_atm_b, color = "B")) +
  ggtitle("PM2.5 per channel from 5/20/26 to 6/1/26", subtitle = unique(mydata_split[[i]]$mac_address)) + 
  xlab("Observation Day") + ylab("PM2.5 Concentration (ug/m3)") +
  scale_x_datetime(date_breaks="2 days") + 
  #scale_color_manual(values=met.brewer("Java")) +
  theme(plot.title = element_text(hjust = 0.5)) +
  theme(plot.subtitle = element_text(hjust = 0.5, color="grey32")) +
  theme(axis.title.y = element_text(vjust = 0.5)) +
  guides(colour = guide_legend(title = "Channel", override.aes = list(size=5,stroke=2,alpha=1)))
}) 
```
``` {r, fig.show="hold", out.width="50%", warning=FALSE, message=FALSE}
indiv_plots <- lapply(channel_plots_time_series,plot)
```


``` {r, fig.show="hold", out.width="50%", warning=FALSE, message=FALSE}
ggplot(f0_24_f9_c6_c8_85_low) + 
  geom_point(aes(x = DateTime, y = pm2_5_atm, color = "A")) +
  geom_point(aes(x = DateTime, y = pm2_5_atm_b, color = "B")) +
  ggtitle("PM2.5 per channel from 5/20/26 to 6/1/26, >250um/m3 filtered out", subtitle = unique(f0_24_f9_c6_c8_85_low$mac_address)) + 
  xlab("Observation Day") + ylab("PM2.5 Concentration (ug/m3)") +
  scale_x_datetime(date_breaks="2 days") + 
  #scale_color_manual(values=met.brewer("Java")) +
  theme(plot.title = element_text(hjust = 0.5)) +
  theme(plot.subtitle = element_text(hjust = 0.5, color="grey32")) +
  theme(axis.title.y = element_text(vjust = 0.5)) +
  guides(colour = guide_legend(title = "Channel", override.aes = list(size=5,stroke=2,alpha=1)))
```